Estimation below the detection limit with application to cryo-em

### 2018-08-07 TEX/inverse_problem_draft.tex
updated figures for the 2-D example (no tex editing for now)
outline of the inverse problems draft

@@

\subsection{Related work} \label{sec:related_literature}

\paragraph{System identification.}

\paragraph{Likelihood-based methods.}

In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}. The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}. However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets. 
%
%%%Interestingly, expectation-maximization (EM)---a popular algorithm for similar estimation problems, such as Gaussian mixture models and multireference alignment---is intractable for this problem. This is true even if  $K=1$ and the number of signal occurrences $M$ is known.
%
Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.

\section{Model} \label{sec:model}

@@

%In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular, we assume that
%\begin{align}
%  \vert i-j \vert\geq 2L-1,   \quad \text{for all } i,j\in\mathcal{S} \text{ such that } i\neq j.
%  \label{eq:spacing}
%\end{align}
%The goal is to estimate $x_1,\ldots,x_K$ from $y$.

%
%\section{Autocorrelation analysis}   \label{sec:autocorrelation}
%
%Our method for estimating the signals is composed of two stages. 
%First, we use the autocorrelation functions of the data to estimate a mixture (i.e., linear combination) of the $K$ signal's autocorrelations. The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the spacing condition~\eqref{eq:spacing} is met. Then, we  use a nonconvex LS  to estimate the signals from their mixed autocorrelations. 
%In this section, we elaborate on the autocorrelation functions and their estimations, while the precise recovery procedure, based on nonconvex optimization, will be discussed in detail in the next section.

@@

\paragraph{Aperiodic autocorrelation functions}
%\subsection{Aperiodic autocorrelation functions} \label{sec:aperiodic_ac}

%\TODO{$L$ is a bad notation here since it could be L or n; and k is poor notation too because we use it to sum up to K.}

@@

\paragraph{Estimating the autocorrelation function of a single signal.}

@@

\paragraph{Estimating the autocorrelation function of multiple signals.}

@@

@@

\paragraph{The impossibility of detection in low $\SNR$.}
If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible. To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$. Suppose too that the oracle provides us with $x$ itself. That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations. This is an easier problem than detecting the support of $s$. Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}. Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.

@@

\paragraph{Estimating a signal from its third-order autocorrelation.}

@@

\paragraph{Identifiability of parameters from the moments of $y$.}

>>>>

We consider the problem of estimating a signal from its multiple occurrences in a measurement. In the high SNR regime, the problem is easy. In the low SNR, it becomes interesting and that is the focus of this paper.

The problem can be posed as blind deconvolution between the signal and a sparse binary signal.
We can also consider the extension for multiple signals.

@@

\subsection{Model}

@@

\subsection{Related work}

In special cases, including the case where $w$ is binary, expectation maximization (EM) has been used~\cite{cappe1999simulation}. The EM method for discrete $w$ is based upon a certain ``forward-backward'' procedure used in hidden Markov models~\cite{rabiner1989tutorial}. However, the complexity of this procedure is nonlinear in $N$, and therefore its usage is limited for big data sets.

Indeed, on each iteration of EM, a probability must be assigned to any feasible combination of positions for the current signal estimate in $M$ locations on the grid $\{1,\ldots,N\}$.
In total, even when excluding forbidden combinations due to the spacing constraint, there are $O(N^M)$ such combinations, and the problem becomes computationally intractable when $M$ grows with $N$ and $N$ is large.

\subsection{Main motivation: The cryo-EM problem}

@@

@@

\subsection{The single signal case}

@@

\subsection{The single signal case}

@@

\subsection{Poisson model (rename)}

@@

If $K=1$ and $x$ is known, then the locations $s_i$ can be estimated via linear programming  in the high $\SNR$ regime~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible. To see this, suppose that an oracle provides us $M$ windows of length $W>L$, each containing exactly one copy of $x$. Suppose too that the oracle provides us with $x$ itself. That is to say, we get a series of windows of length $W$, each one containing a signal $x$ at an unknown location; and our only task is to estimate the locations. This is an easier problem than detecting the support of $s$. Nevertheless, even this simpler problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}. Consequently, detecting the nonzero values of $s$ is impossible in low $\SNR$.

@@

@@
